%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AJY Resume (full)
% Version 0.0 (2019-05-12)
%
% Author:
% Andrew J. Young (andrewjunyoung1@gmail.com)
%
% License:
% None
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Begin Packages and document configuration %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{multicol}

\name{Andrew J. Young} % Your name
\address{(+44)79 1406 9349 \\ % Phone number
         andrewjunyoung1@gmail.com \\ % Email
         bit.ly/ajylinkedin} % Github resume

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Packages and document configuration %%
%% Begin Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Background}

{\bf Imperial College London} \hfill \\
Computer Science and Mathematics (BEng)\\

%% Begin Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Interests (in no order)}:
  Algorithms (High-performance, high-assurance),
  Optimization,
  Security,
  Cryptography,
  Data science and ML

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Interests %%

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Education %%
%% Begin Previous employment %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Experience}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Global Technology Infrastructure, JPMorgan Chase}
    {from 2019}{Software Developer}{London, UK}
  \item Worked on a framework to detect and resolve when actual system state differs
    from desired system state.
  \item Worked on compilation; parsing; identity; events; database management; python.
  \item Built and managed a consumer facing API for describing desired system
    state. 0 to production API in 3 months.
  \item Trained in agile; certified in application security and threat modeling.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Workspace analytics, BP}
    {2018}{Data analytics}{London, UK}
  \item Tasked with learning about employee habits using 3 months of data
    collected from the workplace.
  \item Used python and R to discover and visualize patterns in data and present
    these to clients.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Quantitative Risk (qRisk), JPMorgan Chase}{2018}
    {Software Developer}{London, UK}
    \item Designed and wrote the overnight batch process for the company's risk
      platform.
    \item Wrote optimized python code to interact with existing APIs and legacy
      code.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Opesci Group, Imperial College London}
    {2017}{Research Intern}{London, UK}
      \item Made tutorials in Jupyter notebooks for solving complex ODEs.
      \item Worked in python to solve reaction diffusion problems using the
      team's package and added to the code base.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Hoteling}
    {2016}{Asakusa Guest House Manager}{Tokyo, JP}
      \item Managed a 4 story guest house, developed a language acquisition
      program for international students, and performed English-Japanese-Chinese
      translation.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  %\begin{rSubsection}{Queen Elizabeth's School}{Volunteer Japanese
  %  Teacher}{London, UK}
  %    \item Ran weekly lessons and taught a class of students Japanese to enable
  %    them to pass the JLPT N5.
  %    \item Organized a letter exchange program with a high school in Tokyo.
  %\end{rSubsection}

  %-------------------------------------------------------------------------------

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Previous employment %%
%% Begin Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Projects}

  \item \textbf{\textit{Symboard (Python)}} A text-based keyboard creator which
    allows users to create fully functional, UNIX compatible keylayout files
    using a concise, user-defined specification.
  \item \textbf{\textit{MVL (Multi Valued Logic) (Python)}} Wrote a package to
    implement multi valued logic systems in python.
  \item \textbf{\textit{FlowMonster (Java, Spring Boot)}} Designed and wrote a
    trading robot to participate in market simulations against other teams. Won
    in my team's division and progressed to the finals.
  \item \textbf{\textit{An investigation into membership inference attacks on
    big data (BEng thesis)}} Implemented and optimized a membership inference
    attack using supervised and unsupervised machine learning. Used 2 data sets
    (taxi and telecoms data) to determine if an individual was sampled to
    calculate a summary statistic. Analyzed the performance of the attack
    under different conditions.
  \item \textbf{\textit{Quest.io} (Javascript)} Made a web application using
    React Native, mongoDB, and Google APIs for tourist groups to plan daily
    travel routes. Implemented voting, a chat, and a route planning algorithm.
  \item \textbf{\textit{Pintos} (C)} Built on top of a legacy code base in
    order to produce a fully functional concurrent OS.
  \item \textbf{\textit{PlugInBaby} (Python, node.js)} An IOTA (IoT
    cryptocurrency) application which finds charging stations and
    automatically transacts for electricity on the IOTA tangle. Designed in
    cooperation with the IOTA developers.
  \item \textbf{\textit{WACC compiler} (C)} Designed and built a compiler and
    code-generator from WACC into Arm11.
  %\item \textbf{\textit{Arm11 compiler} (C)} Built a compiler into C for the
  %  Arm11 language with code compiling on a raspberry pi.

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Projects %%
%% Begin Achievements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Achievements}
    %\item \textbf{\textit{2019}{"FlowMonster" finalist}} Won my team's division
    %  and progressed to the finals in a trading robot competition.
    \item \textbf{\textit{2017} IOTA Hack winner}
    Designed and built the winning design, which finds charging stations and
    transacts for electricity automatically on the IOTA tangle.
    \item \textbf{\textit{2016} Built and launched an H-class high-powered
      rocket} in a team of 4. Apogee was reached at 1.5 km before returning to
      ground in a state fit for reuse.
    %\item \textbf{\textit{2016} Scored in the 94th percentile in the JLPT N2
    %  exam.}
    %\item \textbf{\textit{2015} Completed the UCL-Japan Young Challenge},
    %participating in a cultural exchange and Japanese language programs in the
    %UK.
    \item \textbf{\textit{2014} President and founder of an ISSDC finalist
      team.}
    Founded an independent finalist team to the International Space Settlement
    Design Competition. Elected company president at the national and
    international finals.
    %\item \textbf{\textit{2014} Grade 8 Cello with distinction}
\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Achievements %%
%% Begin Technical skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Skills}

  \begin{center}
  \begin{tabular}{ c c c c c c c }
   \textbf{English} & \textbf{Japanese} & \textbf{Chinese} & \textbf{French} &
    \textbf{Spanish} & \textbf{Polish} & \textbf{German} \\
    Native & Fluent (C2) & Intermediate (B2) & Intermediate (B1) & Basic (A2) & Basic
    (A2) & Basic (A2)
  \end{tabular}
  \end{center}

  \item \textbf{Expert in}
    C,
    Java,
    Spring boot,
    \LaTeX,
    Linux,
    Python,
    SQL,
    UNIX,
    Windows,
    Git,
    Jetbrains IDEs,
    Jupyter notebook,
    Vim,

  \item \textbf{In-depth knowledge of}
    CSS,
    Haskell,
    Django,
    Django rest framework,
    Javascript,
    Prolog,
    R,
    x86 Assembly,
    PostgreSQL,
    Scikit-learn
    Gnu bison,

  \item \textbf{Experience with}
    Kafka,
    Azure cloud stack,
    AWS,
    Cloud foundry,
    React (native),
    Dolphin (python),
    Devito (python),

  \item \textbf{Core competencies}:
    Agile methodologies;
    Data science;
    Network, web, and application security (SQL, Javascript, PHP),
    Project management;
    Software architecture

  %\item \textbf{Typing}: 135 wpm (eng), 100 wpm (jpn)

  \item \textbf{First aid}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Technical skills %%

\end{document}
