\documentclass{article}

%%%% Begin package imports %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Language and font encodings
\usepackage[english]{babel}
% Set page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\setcounter{secnumdepth}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End package imports %%%%
%%%% Begin document contents %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\section{Cover Letter}

Each project I have worked on has taught me lessons. I feel that the traits
which I value most in myself are self-reflection, communication, and
management, and I believe that these skills make me stand out most as a
professional, above any specific technical skills. I would like to justify why
I value each of these traits, and give some anecdotes of my experience in doing
so.\\

Self-reflection has brought about so much of my personal growth.
I use self-reflection in the form of writing regular reviews and learning
from each of my mistakes and experiences, good and bad, and spotting trends in
my performance. This learning \textit{how} to learn was perhaps
my biggest lesson from my time at JPMorgan Chase, where I learned and honed
this skill. As a result of weekly reflection, planning, and record keeping, I
was able to take on a large amount of responsibility and complexity --
organizing and chairing meetings with clients, my team, and supervisors, and
ultimately delivering a batch to production. I am certain that self-reflection
will allow me to play to my strengths, learn from mistakes, and sustain growth
throughout my future employment.\\

In every project I have been on, the project's success can be attributed in
great part to the group's successful communication. I have learned the value of
communicating effectively and concisely, in particular from my time as
president of my team in the International Space Settlement Design Competition.
Presiding over a team of 50, I saw that setting clear objectives for each team,
effective organizational structure, and exchanging ideas were the decisive
factors of the competition. Through this I have come to greatly value open and
clear communication with my coworkers and clients.\\

Furthermore, how to manage teams, and myself, has been a key factor in all
projects I have worked on. I feel that understanding the role of each person
and team inside an organization will make teams efficient and cooperative.
I found that my team within JPMorgan showed what good management and incentives
can do to improve team cohesion and efficiency. I admired how thoroughly my
team had adopted agile techniques, the short-and-sweet approach to meetings,
and a desire to shine as individuals and in our team's final product. Above
all, the project leader's experience and direction felt non-egotistical,
well-informed, and thoughtful, as I feel is best.\\

My philosophy of software engineering has grown to be treating code with
certain values in mind. To me, good software not only works but has the
assurance that it does what it is expected to. Good software is simple, clear,
and flexible.  Meanwhile, I place a great personal value on high performance
code, that is well optimized for the environment it will run in. These values
lead me to believe that I would be well suited to be a software engineer at
Twitter.\\

Twitter is a dynamic and innovative company. Its innovations in artificial
intelligence are world leading, and I want to contribute to this.  I believe my
background in mathematics and computing gives me an edge in working in these
fields, where I hope to build on the incredible work Twitter has already done.\\

I respect that Twitter places a strong value on freedom and expression
as a part of its culture. As something I myself value, this makes me confident
that I will fit in working at Twitter. Furthermore, I believe that my strengths
in self-reflection, communication, and management will become increasingly
important, in complement to my ability as a software developer.\\

I look forward to hearing from you in due course.\\

Kind regards,\\

Andrew J. Young\\

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End document contents %%%%
