%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% XUN Jianli (XUN Curriculum Vitae)
% Version 0.0 (2017-07-17)
% 
% Author:
% Andrew Jun Young (andrewjunyoung1@gmail.com)
% 
% License: 
% None
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Packages and document configurations

\documentclass[10pt,a4paper]{article}
\include{structure}

\usepackage{multicol}

\begin{document}

%-------------------------------------------------------------------------------
% Name And Contact Information
%-------------------------------------------------------------------------------

\header{Andrew J. Young}

\noindent\href{mailto:andrew-young16@imperial.ac.uk}{andrew-young16@imperial.ac.uk}\bull
+44 79 1406 9349\bull
%\href{http://www.andrewjunyoung.com}{www.andrewjunyoung.com}
\\

25 Moffats Lane\bull Hatfield\bull HERTS\bull AL9 7RX

\spacedhrule{0.9em}{-0.4em}

%-------------------------------------------------------------------------------
% Education
%-------------------------------------------------------------------------------

\begin{section}{Education}

\textsc{\textbf{Imperial College London}}
Computer Science and Mathematics (MEng)
Member to Debating Society, Dept. of Computing Society, Mathematics Society, 
Imperial Snowsports, Finance \& Investment Society

\textsc{\textbf{Queen Elizabeth's School, Barnet}}
A2: 4 A\*s in Math, Further Math, Physics, and Chemistry
GCSE: 13 A\^s

%-------------------------------------------------------------------------------
% Professional Experience
%-------------------------------------------------------------------------------

\begin{section}{Professional Experience}

    \begin{rSubsection}{Opesci Group, Imperial College London}{May 2017 - Aug 2017}{Research Intern}{London, UK}
\begin{itemize}
    \item Worked with Devito, the team's python package for solving finite difference equations.
    \item Made tutorials in jupyter notebooks for solving high-level ODEs.
    \item Extended the application of Devito to solve topology optimization problems and added to the codebase.
\end{itemize}

%-------------------------------------------------------------------------------

\begin{rSubsection}{JPMorgan Chase}{Apr 2017}{Spring into Technology}{London, UK}
\begin{itemize}
    \item Shadowed employees from software divisions and engaged in group coding projects.
\end{itemize}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Morgan Stanley}{Mar 2017}{Spring Insight: Technology}{London, UK}
\begin{itemize}
    \item Shadowed tech divisions and learned about the applications of technology in banks.
\end{itemize}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Hoteling}{Jul 2016 - Sep 2016}{Asakusa Guest House Manager}{Tokyo, JP}
\begin{itemize}
    \item Managed a 4 storey guest house in Tokyo, developed a program for international students to learn foreign languages, and translating between English, Japanese, and Chinese.
\end{itemize}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Queen Elizabeth's School}{Sep 2014 - Jun 2016}{Volunteer Japanese Teacher}{London, UK}
\begin{itemize}
    \item Ran weekly lessons and taught a class of students Japanese to enable them to pass the JLPT N5. Organized a letter exchange program with a high school in Tokyo.
\end{itemize}

%-------------------------------------------------------------------------------

\begin{rSubsection}{BlueCrest Capital Management}{Jul 2014}{Work Experience}{London, UK}
\begin{itemize}
    \item Worked alongside the Volatility Arbitrage Group and shadowed employees in the software division to understand how their system conducts risk analysis
\end{itemize}

%-------------------------------------------------------------------------------
% Achievements
%-------------------------------------------------------------------------------

\begin{itemize}
    \item \textbf{\textit{2016} Constructed and launched an H-class high-powered rocket} in a team of 4. Apogee was reached at 1.5 km before returning to ground in a state fit for reuse.
    \item \textbf{\textit{2015} Completed the UCL-Japan Young Challenge}, participating in a cultural exchange and Japanese language programs in the UK.
    \item \textbf{\textit{2014} President and founder of an ISSDC finalist team.} Founded an independent finalist team to the International Space Settlement Design Competition. Elected company president at the national and international finals.
    \item \textbf{\textit{2014} Grade 8 Cello with distinction}
\end{itemize}

% The languages and technical skills sections will appear side-by-side
\begin{multicols}{3}

%-------------------------------------------------------------------------------
% Languages
%-------------------------------------------------------------------------------
\textbf{English:} Native
\textbf{Japanese:} Fluent (N2: 94th pctl)
\textbf{Chinese:} Intermediate
\textbf{French:} Basic
\textbf{German:} Basic

\columnbreak
%-------------------------------------------------------------------------------
% Technical Skills
%-------------------------------------------------------------------------------
\textbf{Software Langs:} 
    Java, HTML, Python, Haskell, CSS, \LaTeX, x86 Assembly, C, mySQL
\textbf{Software Tools:} 
    MS Office, MacOS, Linux, Git, Windows, Vim, Emacs, Intellij IDEA, jupyter notebook
\textbf{Protocols \& APIs}: 
    JSON
\textbf{Typing:} 135 wpm (eng), 150 cpm (jpn)

\end{multicols}

\end{document}
