%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AJY Resume (full)
% Version 0.0 (2019-05-12)
%
% Author:
% Andrew J. Young (andrewjunyoung1@gmail.com)
%
% License:
% None
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Begin Packages and document configuration %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{multicol}

\name{Andrew J. Young} % Your name
\address{andrewjunyoung1@gmail.com \\ % Email
         bit.ly/ajylinkedin % LinkedIn
         (Please get in touch by email) % Email me man
       }

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Packages and document configuration %%
%% Begin Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Education}

  \begin{center}
  \begin{tabular}{ c c }
    {\bf Imperial College London} & {\bf Queen Elizabeth's School, Barnet} \\
    Computer Science and Mathematics (BEng) -- 2-1 honors &
    A levels -- 4 A*s (highest); GCSE -- 14 A*s (highest) \\
  \end{tabular}
  \end{center}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Education %%
%% Begin Previous employment %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Experience}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Global Technology Infrastructure, JPMorgan Chase}
    {(intern) 2018 Jun - Sep; (full-time) from 2019 Sep}{Software Developer}{London, UK}
  \item Led the team's transition to cloud microservices, designed cloud
    architecture, and wrote the core API package.
  \item Owned a data collection component for VMWare hardware. Test coverage 30
    \% $\rightarrow$ 90 \%; runtime 35 times faster
  \item Built customer facing APIs for describing and evaluating system state.
    0 to production API in 3 months.
  \item Trained in agile; certified in application security and threat modeling.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{The Mix}
    {2019 Sep -- 2020 July}{Software Developer}{London, UK}
  \item Worked alongside the charity's development team to migrate their
    APIs to ElasticSearch and AWS lambdas. Improved the relevance of search
    results and handed over the to The Mix in production.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Workspace analytics, BP}
    {2018 Sep - 2019 Jan}{Data analytics}{London, UK}
  \item Used python, R, and ML to find and visualize patterns in employee data,
    and present this to clients.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Opesci Group, Imperial College London}
    {2017 Jun - Sep}{Research Intern}{London, UK}
  \item Used math and python to solve complex ODEs (stencil problems) for
    diffusion, and wrote tutorials in Jupyter.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Hoteling}
    {2016 Jun - Sep}{Asakusa Guest House Manager}{Tokyo, JP}
      \item Managed a 4 story guest house, developed a language acquisition
      program for international students, and performed English-Japanese-Chinese
      translation. Customer reviews of their stay all $\ge 4$ stars.
  \end{rSubsection}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Previous employment %%
%% Begin Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Projects}

  \item \textbf{\textit{LApps}} Made an Android mobile app for retail and
    restaurants with automated cloud deployment and back-end.
  \item \textbf{\textit{Symboard}} Creates installable keyboard layouts from
    user-defined specs. Supports all EU languages.
  %\item \textbf{\textit{MVL (Multi Valued Logic)}} Implements multi valued logic
  %  systems in python.
  %\item \textbf{\textit{FlowMonster}} Designed and wrote a trading robot to
  %  compete in market simulations against other teams. Won in my team's
  %  division and progressed to the finals.
  \item \textbf{\textit{An investigation into membership inference attacks on
    big data (BEng thesis)}} -- \textit{First class honors} Implemented,
    optimized, and analyzed an attack on user privacy using ML. Reduced run time
    by 75 \%, leaked info about individual taxi locations in data sets of >
    30,000 taxis, and added defenses which negate this attack.
  \item \textbf{\textit{Quest.io}} Made a cross platform app using
    React Native, mongoDB, and Google APIs for tourist groups to plan daily
    travel routes. Implemented voting, a chat, and a route planning algorithm.
  %\item \textbf{\textit{Pintos} (C)} Built on top of a legacy code base in
  %  order to produce a fully functional concurrent OS.
  %\item \textbf{\textit{PlugInBaby} (Python, node.js)} An IOTA (IoT
  %  cryptocurrency) application which finds charging stations and
  %  automatically transacts for electricity on the IOTA tangle. Winning project
  %  of IOTA Hack 2017.
  %\item \textbf{\textit{WACC compiler} (C)} Designed and built a compiler and
  %  code-generator from WACC into Arm11.
  %\item \textbf{\textit{Arm11 compiler} (C)} Built a compiler into C for the
  %  Arm11 language with code compiling on a raspberry pi.
  \item \textbf{\textit{Built and launched an H-class high powered rocket}}.
    Apogee was reached at 1.5 km before returning to ground in a
    state fit for reuse. I keep the rocket in my living room.

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Projects %%
%% Begin Technical skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Skills}

  \begin{center}
  \begin{tabular}{ c c c c c c c }
   \textbf{English} & \textbf{Japanese} & \textbf{Chinese} & \textbf{French} &
    \textbf{Spanish} & \textbf{Polish} & \textbf{German} \\
    Native & Fluent (C2) & Intermediate (B2) & Intermediate (B1) & Basic (A2) & Basic
    (A2) & Basic (A2)
  \end{tabular}
  \end{center}

  \item \textbf{Expert in}
    Kotlin;
    Spring boot;
    Android;
    Python;
    Django;
    DRF;
    Java;
    C;
    %\LaTeX,
    Linux;
    SQL;
    UNIX;
    %Windows;
    Git;
    %Jupyter notebook,
    %Vim,
    Cloud foundry,

  %\item \textbf{In-depth knowledge of}
    %CSS,
    %Haskell,
    %Prolog,
    %Scikit-learn,
    %Gnu bison,

  \item \textbf{Experience with}
    R,
    %x86 Assembly,
    Javascript;
    Mobile, web front end;
    noSQL;
    Kafka;
    Azure cloud stack;
    AWS;
    React (native);

  %\item \textbf{Core competencies}:
  %  Agile;
  %  Data science;
  %  Network, web, app security;
  %  Project management;
  %  Cloud

  %\item \textbf{Typing}: 135 wpm (eng), 100 wpm (jpn)

  \item \textbf{First aid}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Technical skills %%

\end{document}
