%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AJY Resume (full)
% Version 0.0 (2019-05-12)
%
% Author:
% Andrew J. Young (andrewjunyoung1@gmail.com)
%
% License:
% None
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Begin Packages and document configuration %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{multicol}

\name{Andrew J. Young} % Your name
\address{(+1) 862-363-0602 \\ % Phone number
         andrewjunyoung1@gmail.com % Email
         bit.ly/ajylinkedin} % LinkedIn

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Packages and document configuration %%
%% Begin Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Education}

\begin{center}
\begin{tabular}{ l l }
 \textbf{Imperial College London} & \textbf{Queen Elizabeth's School, Barnet} \\
  Computer Science and Mathematics (BEng) -- 2-1 honors &
  A-levels: 4 A*s (highest); GCSE: 13 A*s (highest)
\end{tabular}
\end{center}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Education %%
%% Begin Previous employment %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Experience}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Get Instant Inc.}
    {Founder \& CTO}{from Nov 2021}{Toronto, ON}
  \item Worked with quick service restaurants to build a solution to cut dropoff
    in checkout, and to developed a mobile app; app clip; and API.
  \item Pitched to investors and sold to customers. Onboarded 2 businesses;
    backed by Entrepreneur First.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Sierra Compute Limited}
    {Founder}{2021 Jan - Nov}{London, UK}
  \item Worked with SMEs to replace POS hardware with mobile SAAS solutions.
  \item Onboarded over 50 businesses; processed payments for 2.
  \item Reused this same platform to build automation solutions for a client to
    securely trade crypto.
  \item Built Android and iOS apps in 1 month each; set up and automated a
    server with AWS infra (Cognito; Lambdas; Secrets)
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{JPMorgan Chase, Virtual Infrastructure}
    {Software Developer}{2019 Sep - 2020 Dec}{London, UK}
  \item Managed virtual DB infrastructure using DRF. Built an audit tool
    used for managing cloud resources, reporting, event raising. Also used
    compilation and parsing, identity, DB management, SQL, python, and cloud.
  \item Built and managed a consumer facing API. 0 to production API in 3 months.
  \item Trained in agile; certified in application security and threat modeling.
  \item Onboarded and managed the work of 2 junior team members.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{The Mix}
    {Software Developer}{Sep 2019 - Jun 2020}{London, UK}
  \item Worked in an agile team implementing search functionality across their
    existing APIs using ElasticSearch and AWS lambdas, triggered by Cloud Watch
    events.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{BP, Workspace analytics}
    {Data Analyst}{2018 Oct - Jan}{London, UK}
  \item Given 3 months of employee data, did data analysis and machine learning
    on this data to present to clients. Used python and R, visualization, cloud
    (Azure), and SQL.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{JPMorgan Chase, Quantitative Risk}
    {Software Developer}{2018 Jun - Sep}{London, UK}
    \item Worked on an agile team optimizing batch operations of financial
      derivatives that calculated risk and price. Written in python, and
      using Kafka, and database management (Cassandra) with a legacy code base.
  \end{rSubsection}

  %-------------------------------------------------------------------------------

  \begin{rSubsection}{Imperial College London, Opesci Group}
    {Research Intern}{2017 Jun - Sep}{London, UK}
      \item Used calculus, python and jupyter notebooks to solve complex ODEs,
        and improve the team's calculation engine.
  \end{rSubsection}

  %-------------------------------------------------------------------------------
 %
  %\begin{rSubsection}{Hoteling}
  %  {Asakusa Guest House Manager}{2016 July - Sep}{Tokyo, JP}
  %    \item Managed a 4 story guest house, developed a language acquisition
  %    program for international students, and performed English-Japanese-Chinese
  %    translation.
  %\end{rSubsection}
  %
  %-------------------------------------------------------------------------------
  %
  %\begin{rSubsection}{Queen Elizabeth's School}{Japanese Teacher}
  %  {}{London, UK}
  %    \item Ran weekly lessons and taught a class of students Japanese to enable
  %    them to pass the JLPT N5.
  %    \item Organized a letter exchange program with a high school in Tokyo.
  %\end{rSubsection}
  %
  %-------------------------------------------------------------------------------

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Previous employment %%
%% Begin Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Projects}

  \item \textbf{\textit{Symboard (Python)}} A text-based keyboard creator which
    allows users to create fully functional, UNIX compatible keylayout files
    using a concise, user-defined specification.
  \item \textbf{\textit{MVL (Multi Valued Logic) (Python)}} Wrote a package to
    implement multi valued logic systems in python.
  \item \textbf{\textit{FlowMonster (Java, Spring Boot)}} Designed and wrote a
    trading robot to participate in market simulations against other teams.
  \item \textbf{\textit{An investigation into membership inference attacks on
    big data (BEng thesis)}} Implemented and optimized a membership inference
    attack using supervised and unsupervised machine learning. Used 2 data sets
    (taxi and telecoms data) to determine if an individual was sampled to
    calculate a summary statistic. Analyzed the performance of the attack
    under different conditions.
  \item \textbf{\textit{Quest.io} (Javascript)} Made a web application using
    React Native, mongoDB, and Google APIs for tourist groups to plan daily
    travel routes. Implemented voting, a chat, and a route planning algorithm.
  \item \textbf{\textit{Pintos} (C)} Built on top of a legacy code base in
    order to produce a fully functional concurrent OS.
  \item \textbf{\textit{PlugInBaby} (Python, node.js)} An IOTA (IoT
    cryptocurrency) application which finds charging stations and
    automatically transacts for electricity on the IOTA tangle. Designed in
    cooperation with the IOTA developers.
  \item \textbf{\textit{WACC compiler} (C)} Designed and built a compiler and
    code-generator from WACC into Arm11.
  \item \textbf{\textit{Arm11 compiler} (C)} Built a compiler into C for the
    Arm11 language with code compiling on a raspberry pi.

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Projects %%
%% Begin Achievements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{rSection}{Achievements}
%    \item \textbf{\textit{2019}{"FlowMonster" finalist}} Won my team's division
%      and progressed to the finals in a trading robot competition.
%    \item \textbf{\textit{2017} IOTA Hack winner}
%      Designed and built the winning design, which finds charging stations and
%      transacts for electricity automatically on the IOTA tangle.
%    \item \textbf{\textit{2016} Built and launched an H-class high-powered
%      rocket} in a team of 4. Apogee was reached at 1.5 km before returning to
%      ground in a state fit for reuse.
%    \item \textbf{\textit{2016} Scored in the 94th percentile in the JLPT N2
%      exam.}
%    \item \textbf{\textit{2015} Completed the UCL-Japan Young Challenge},
%    participating in a cultural exchange and Japanese language programs in the
%    UK.
%    \item \textbf{\textit{2014} President and founder of an ISSDC finalist
%      team.}
%    Founded an independent finalist team to the International Space Settlement
%    Design Competition. Elected company president at the national and
%    international finals.
%     \item \textbf{\textit{2014} Grade 8 Cello with distinction}
%\end{rSection}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Achievements %%
%% Begin Technical skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{rSection}{Skills}

  \begin{center}
  \begin{tabular}{ c c c c c c c }
   \textbf{English} & \textbf{Japanese} & \textbf{Chinese} & \textbf{French} &
    \textbf{Spanish} & \textbf{Polish} & \textbf{German} \\
    Native & Fluent (C2) & Intermediate (B2) & Intermediate (B1) & Basic (A2) & Basic
    (A2) & Basic (A2)
  \end{tabular}
  \end{center}

  \item \textbf{Expert in}
    C,
    Java,
    Spring boot,
    \LaTeX,
    Linux,
    Python,
    SQL,
    UNIX,
    Windows,
    Git,
    Jetbrains IDEs,
    Jupyter notebook,
    Vim,
    Swift,
    iOS development,

  \item \textbf{In-depth knowledge of}
    Android development,
    CSS,
    Haskell,
    Django,
    Django rest framework,
    Javascript,
    Prolog,
    R,
    x86 Assembly,
    PostgreSQL,
    Scikit-learn
    Gnu bison,

  \item \textbf{Experience with}
    Kafka,
    Azure cloud stack,
    AWS,
    Cloud foundry,
    React (native),
    Dolphin (python),
    Devito (python),

  \item \textbf{Core competencies}:
    Software development;
    Project management;
    Network, web, and application security (SQL, Javascript, PHP);
    Data science;

  \item \textbf{Typing}: 142 wpm (eng), 100 wpm (jpn)

  \item \textbf{First aid}

\end{rSection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% End Technical skills %%

\end{document}
