%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AJY Curriculum Vitae
% Version 0.0 (2017-07-17)
%
% Author:
% Andrew Jun Young (andrew.young16@imperial.ac.uk)
%
% License:
% None
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{multicol}

\name{Andrew J. Young} % Your name
\address{(+44)7914069349 \\ % Phone number
         andrew.young16@imperial.ac.uk \\ % Email
         bit.ly/ajylinkedin} % LinkedIn

% INTERESTS

\begin{document}

%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Imperial College London} \hfill {\em 2016-2019} \\ 
Computer Science and Mathematics (BEng)\smallskip\\
Societies: Debating, Dept. of Computing (DoCSoc), Mathematics, Finance,
Investment

{\bf Queen Elizabeth's School, Barnet} \hfill {\em 2009-2016} \\ 
A2: 4 A*s (highest) in Math, Further Math, Physics, and Chemistry; GCSE: 13 A*s (highest)

% INTERESTS

\textbf{Interests (no particular order)}:
  Algorithms (High-performance, high-assurance, financial),
  AI (Reinforcement learning, deep learning),
  Security \& cryptography,
  Big data,
  Quantum computing (algorithms, security).

\end{rSection}

%-------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%-------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Quantitative Risk (qRisk), JPMorgan Chase}{Jun 2018-Aug 2018}{Software
Developer}{London, UK}
  \item Created the overnight batch process for the company's risk platform.
  \item Developed high performance python code to interact with existing APIs
and legacy code to run the batch.
\end{rSubsection}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Opesci Group, Imperial College London}{May 2017 - Aug 2017}{Research Intern}{London, UK}
    \item Made tutorials in Jupyter notebooks for solving complex ODEs.
    \item Worked in python to solve reaction diffusion problems using the
    team's package and added to the codebase.
\end{rSubsection}

%-------------------------------------------------------------------------------

\begin{rSubsection}{JPMorgan Chase}{Apr 2017}{Spring into Technology}{London, UK}
    \item Shadowed employees from software divisions and engaged in group
    coding projects.
\end{rSubsection}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Morgan Stanley}{Mar 2017}{Spring Insight: Technology}{London, UK}
    \item Shadowed tech divisions and learned about the applications of
    technology in banks.
\end{rSubsection}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Hoteling}{Jul 2016 - Sep 2016}{Asakusa Guest House Manager}{Tokyo, JP}
    \item Managed a 4 story guest house, developed a language acquisition
    program for international students, and performed English-Japanese-Chinese
    translation.
\end{rSubsection}

%-------------------------------------------------------------------------------

\begin{rSubsection}{Queen Elizabeth's School}{Sep 2014 - Jun 2016}{Volunteer Japanese Teacher}{London, UK}
    \item Ran weekly lessons and taught a class of students Japanese to enable
    them to pass the JLPT N5.
    \item Organized a letter exchange program with a high school in Tokyo.
\end{rSubsection}

%-------------------------------------------------------------------------------

\begin{rSubsection}{BlueCrest Capital Management}{Jul 2014}{Work Experience}{London, UK}
    \item Shadowed employees of the Volatility Arbitrage Group and technology
    teams.
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
% Projects
%-------------------------------------------------------------------------------

\begin{rSection}{Projects}
    \item \textbf{\textit{Quest.io} (Javascript)} Created a web application
    using React Native, mongoDB, and google APIs which implemented a voting
    platform, chat, and a route planning algorithm for groups to plan daily
    travel routes.
    \item \textbf{\textit{Pintos} (C)} Built on top of a legacy code base in
    order to produce a fully functional concurrent OS.
    \item \textbf{\textit{PlugInBaby} (Python, node.js)} An IOTA (IoT
    cryptocurrency) application which finds charging stations and transacts for
    electricity automatically on the IOTA tangle. Designed in cooperation with
    the IOTA developers.
    \item \textbf{\textit{WACC compiler} (C)} Designed and built a compiler and
    code-generator from WACC into Arm11.
    \item \textbf{\textit{Arm11 compiler} (C)} Built a compiler into C for the
    Arm11 language with code compiling on a raspberry pi.
\end{rSection}

%-------------------------------------------------------------------------------
% Achievements
%-------------------------------------------------------------------------------

\begin{rSection}{Achievements}
    \item \textbf{\textit{2017} IOTA Hack winner}
    Designed and built the winning design, which finds charging stations and
    transacts for electricity automatically on the IOTA tangle.
    \item \textbf{\textit{2016} Constructed and launched an H-class high-powered rocket}
    in a team of 4. Apogee was reached at 1.5 km before returning to ground in
    a state fit for reuse.
    \item \textbf{\textit{2016} Scored in the 94th percentile in the JLPT N2 exam.}
    \item \textbf{\textit{2015} Completed the UCL-Japan Young Challenge},
    participating in a cultural exchange and Japanese language programs in the
    UK.
    \item \textbf{\textit{2014} President and founder of an ISSDC finalist team.}
    Founded an independent finalist team to the International Space Settlement
    Design Competition. Elected company president at the national and
    international finals.
    \item \textbf{\textit{2014} Grade 8 Cello with distinction}
\end{rSection}

%-------------------------------------------------------------------------------
% Languages
%-------------------------------------------------------------------------------

\begin{rSection}{Languages}

\begin{center}
\begin{tabular}{ c c c c c c }
 \textbf{English} & \textbf{Japanese} & \textbf{Chinese} & \textbf{French} &
 \textbf{Spanish} & \textbf{German} \\
 Native & Fluent (C1) & Intermediate (B2) & Basic (B1) & Basic (A2) & Basic (A2)
\end{tabular}
\end{center}

\end{rSection}

%-------------------------------------------------------------------------------
% Technical skills
%-------------------------------------------------------------------------------

\begin{rSection}{Technical skills}
    \item \textbf{Software Langs:}
        C,
        CSS,
        HTML,
        Haskell,
        Java,
        Javascript,
        \LaTeX,
        Prolog,
        Python,
        (no)SQL,
        Scala,
        x86 Assembly
    \item \textbf{Software Tools:}
        % Programs
        Emacs,
        JetBrains IDEs,
        Vim
        MS Office,
        % OS
        Linux,
        MacOS,
        Windows,
        % Packages
        Git,
        Jupyter notebook,
        Node.js,
        React (Native)
    \item \textbf{Typing:} 135 wpm (eng), 100 wpm (jpn)
\end{rSection}

%----------------------------------------------------------------------------------------
% Other
%----------------------------------------------------------------------------------------

\end{document}
